Probing the Deuteron at Very Large Internal Momenta

### 2020-08-07 MY_PUBLICATIONS/PRL/FINAL_DRAFT/MARKED_PRL/introduction.tex
updated

practically unexplored and not well understood. At such small inter-nucleon distances, the nucleon-nucleon (NN) interaction is expected to become repulsive and the interacting
nucleons begin to overlap. The dynamics in this short distance region are directly related to the dynamics of two-nucleon short range correlations (SRC) observed in $A>2$ nuclei \cite{PhysRevC.68.014313,PhysRevLett.96.082501,PhysRevLett.99.072501,Fomin_2017,Barack_2019,RevModPhys.89.045002}.

@@

which a transition between nucleonic to quark degrees of freedom has been observed \cite{PhysRevLett.81.4576,PhysRevLett.87.102302,PhysRevC.66.042201}. \\
\indent The most direct way to study the short range structure of the deuteron wave function (or equivalently, its high momentum components) is via the exclusive deuteron
electro-disintegration reaction at internal momenta $p_{\mathrm{r}}>300$ MeV/c. For $^{2}\mathrm{H}(e,e'p)n$, within the PWIA, the virtual photon couples to

@@

\indent In reality, the ejected nucleon undergoes FSI corresponding to subsequent interactions with the recoiling system. Another possibility is that the
photon couples to the virtual meson being exchanged between nucleons (MEC), or that the photon excites a bound nucleon into an isobar resonance state ($\Delta$) which subsequently
decays ($\Delta N\rightarrow NN$) via FSI to the ground state (IC).  FSI, MEC and IC can significantly alter the recoiling neutron

@@

$\Lambda^{2}\sim 0.8-1 $ (GeV/c)$^{2}$ \cite{Sargsian_2001}. IC can be suppressed kinematically by selecting $x_{\mathrm{Bj}}>1$, where one probes the lower energy ($\omega$) part of the deuteron quasi-elastic peak which is maximally away from the inelastic resonance

>>>>

practically unexplored and not well understood. At such small inter-nucleon distances, the nucleon-nucleon ($NN$) interaction is expected to become repulsive and the interacting
nucleons begin to overlap. The dynamics in this short distance region are directly related to the dynamics of two-nucleon short range correlations (SRC) observed in $A>2$ nuclei \cite{PhysRevC.68.014313,PhysRevLett.96.082501,PhysRevLett.99.072501,Fomin_2017,Hen2014,RevModPhys.89.045002}.

@@

which a transition between nucleonic to quark degrees of freedom has been observed \cite{PhysRevLett.81.4576,PhysRevLett.87.102302,PhysRevC.66.042201}.
However, in contrast to SRCs, they were related mostly to the final state structure of nuclei rather than to its initial state (see, e.g., Ref.\cite{PhysRevLett.84.3045}).\\
\indent The most direct way to study the short range structure of the deuteron wave function (or equivalently, its high momentum component) is via the exclusive deuteron
electro-disintegration reaction at internal momenta $p_{\mathrm{r}}>300$ MeV/c. For $^{2}\mathrm{H}(e,e'p)n$, within the plane wave impulse approximation (PWIA), the virtual photon couples to

@@

%\indent In reality, the ejected nucleon undergoes FSI corresponding to subsequent interactions with the recoiling system. Another possibility is that the
%photon couples to the virtual meson being exchanged between nucleons (MEC), or that the photon excites a bound nucleon into an isobar resonance state ($\Delta$) which subsequently
%decays ($\Delta N\rightarrow NN$) via FSI to the ground state (IC).
\indent In addition to PWIA picture, the ejected nucleon undergoes final state interactions (FSI) with the recoiling nucleon. Other contributing processes are
the photon coupling to the exchanged mesons in the $pn$ system, generating meson exchange currents (MEC), or the photon exciting the bound nucleon into the
resonating state (mainly $\Delta$-isobar) with subsequent $\Delta N \to NN$ rescattering, referred to as isobar currents (IC). FSI, MEC and IC can significantly alter the recoiling neutron

@@

$\Lambda^{2}\sim 0.8-1 $ (GeV/c)$^{2}$ \cite{Sargsian_2001}. Note that other meson exchange contributions that take place before the virtual photon interaction are included in the definition of the ground state wave function of the detueron. IC can be suppressed kinematically by selecting $x_{\mathrm{Bj}}>1$, where one probes the lower energy ($\omega$) part of the deuteron quasi-elastic peak which is maximally away from the inelastic resonance

### 2020-08-07 MY_PUBLICATIONS/PRL/FINAL_DRAFT/body.tex
updated

and target boiling ($0.38 \%$) which were added in quadrature and determined to be about 0.81 $\%$ per setting. The systematic uncertainties due to
proton loss in HMS ($0.49 \%$), total live time ($3.0 \%$) and total charge ($2.0\%$) were the same for every setting and thus were added (in quadrature)
as an overall normalization constant to the final result.\\

@@

For $\theta_{nq}= 35^{\circ}, 45^{\circ}$ and $75^{\circ}$ (presented in this Letter) the overall kinematic uncertainty varied up to 6.5$\%$.
The overall systematic uncertainty was determined by the quadrature sum of the normalization and kinematic uncertainties which varied up to 10.6$\%$. This result was then added in quadrature
to the statistical uncertainty (20-30$\%$ on average) to obtain the final uncertainty on the cross sections. \\

>>>>

and target boiling ($0.38 \%$) which were added in quadrature and determined to be about 0.81 $\%$ per setting. This result was then added quadratically to
the systematic uncertainties due to proton loss in HMS ($0.49 \%$), total live time ($3.0 \%$) and total charge ($2.0\%$), which were the same for every setting,
to define the overall normalization uncertainty ($\leq$ 8.4$\%$).\\

@@

For $\theta_{nq}= 35^{\circ}, 45^{\circ}$ and $75^{\circ}$ (presented in this Letter) the overall kinematic uncertainty varied below 6.5$\%$.
The total uncertainty was defined as the quadrature sum of the normalization ($\leq$ 8.4$\%$), kinematic ($\leq$ 6.5$\%$) and statistical ($\sim20-30\%$ on average) uncertainties
to obtain the final uncertainty on the cross sections.\\
%The overall systematic uncertainty was determined by the quadrature sum of the normalization and kinematic uncertainties which varied up to 10.6$\%$. This result was then added in quadrature
%to the statistical uncertainty (20-30$\%$ on average) to obtain the final uncertainty on the cross sections. \\
